Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2023-12-31 src/naomi-simple_ks/ks.Rmd
Final KS figure touches

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq - TMB, col = parname, size = size)) +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = extended_cbpalette(n = 20)) +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32)) +
  geom_abline(slope = 0, intercept = 0, linetype = "dashed") +
  labs(x = "KS(GEB, NUTS)", y = "KS(GPCA-AGHQ, NUTS) - KS(GEB, NUTS)", col = "Parameter", size = "Length") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "vertical"), col = guide_legend(title.position = "top")) +
  theme(legend.position = "bottom", legend.title = element_text(size = rel(0.9)), legend.text = element_text(size = rel(0.65)))

>>>>

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq - TMB, col = parname, size = size)) +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = extended_cbpalette(n = 20)) +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32)) +
  geom_abline(slope = 0, intercept = 0, linetype = "dashed") +
  labs(x = "KS(GEB)", y = "KS(GPCA-AGHQ) - KS(GEB)", col = "Parameter", size = "Length") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "vertical"), col = guide_legend(title.position = "top", nrow = 5, byrow = TRUE)) +
  theme(legend.position = "bottom", legend.title = element_text(size = rel(0.9)), legend.text = element_text(size = rel(0.9)))
